Topic Scores

### 2019-02-20 Topic Scores.Rmd
save key words

kw_stopwords =c(
  "student", "skill", "academic", "bate", "participant", "gain", "primarily", "main", "2016", "action", "level", "issue",
  "concept", "close", "day", "edition", "primary", "project", "method", "apply", "busy", "address", "role", "post", "oxford",
  "cuss", "lecture", "pbl",
    #unsure:
  "theory", "search", "perspective"
                )
kw <- setdiff(top_words, kw_stopwords)
```

>>>>

kw_stopwords =c(
  "student", "skill", "academic", "bate", "participant", "gain", "primarily", "main", "2016", "action", "level", "issue",
  "concept", "close", "day", "edition", "primary", "project", "method", "apply", "busy", "address", "role", "post", "oxford",
  "cuss", "lecture", "pbl",
    #unsure:
  "theory", "search", "perspective"
                )
kw <- setdiff(top_words, kw_stopwords)

save(kw, file="App/Recommender System/LDA_keyword_DELETE_.RDATA")
```
